Classification of RDF Constraint Types to Ensure High Quality of Metadata and Data

### 2015-04-28 paper/paper7/paper7.tex
introduction

The \textbf{contribution} of this paper is the development of a system 
\begin{enumerate}
	\item to classify RDF constraints (according to their severity levels) to evaluate the quality of metadata and data which may be represented by any vocabulary and 
	\item to classify RDF constraint types (according to their complexity) which in most cases correspond to RDF validation requirements\footnote{For simplicity reasons, we use the terms \emph{constraint types} and \emph{constraints} instead of \emph{RDF constraint types} and \emph{RDF constraints} in the rest of the paper} (sections \ref{classification} - \ref{complex-constraint-types}).
\end{enumerate}
By defining a huge amount of constraints of the majority of the constraint types,   
we apply the developed classification system to several and different vocabularies from the \emph{SBE} domain to represent both metadata and data and therefore prove its generality.
A complex and complete real world running example from the \emph{SBE} domain serves to prove the claim that the developed classification system perfectly applies for diverse vocabularies.
%, i.e., that it does not matter which vocabularies are used to represent (meta)data and for which domains constraints are defined.
We describe why RDF validation is important for the \emph{SBE} community (section \ref{motivation}), 
how data in tabular format and metadata on person-level data sets, aggregated data sets, and thesauri are represented in RDF, and how therefore reused vocabularies are interrelated (section \ref{rdf-representation}).
We explain how \emph{SBE} (meta)data is validated against constraints, instantiated from constraint types organized in the classification system, to ensure high quality of and trust in (meta)data.

>>>>

The \textbf{contribution} of this paper is the development of a system 
\begin{enumerate}
	\item to classify RDF constraints (according to their severity levels) to evaluate the quality of metadata and data which may be represented by any vocabulary and 
	\item to classify RDF constraint types (according to their complexity) which in most cases correspond to RDF validation requirements\footnote{For simplicity reasons, we use the terms \emph{constraint types} and \emph{constraints} instead of \emph{RDF constraint types} and \emph{RDF constraints} in the rest of the paper} (sections \ref{classification} - \ref{complex-constraint-types}).
\end{enumerate}
By defining a huge amount of constraints of the majority of the constraint types,   
we apply the developed classification system to several and different vocabularies from the \emph{SBE} domain to represent both metadata and data and therefore prove its generality.
A complex and complete real world running example from the \emph{SBE} domain serves to prove the claim that the developed classification system perfectly applies for diverse vocabularies.
%, i.e., that it does not matter which vocabularies are used to represent (meta)data and for which domains constraints are defined.
We describe why RDF validation is important for the \emph{SBE} community (section \ref{motivation}), 
how data in tabular format and metadata on person-level data sets, aggregated data sets, and thesauri are represented in RDF, 
how therefore reused vocabularies are interrelated (section \ref{rdf-representation}),
and how \emph{SBE} (meta)data is validated against constraints of different constraint types (sections \ref{classification} - \ref{complex-constraint-types}).
